### 2012-03-22 doc/theses/mikula/diplomka.tex
Master thesis: In progress.

@@

%%% Přílohy k diplomové práci, existují-li (různé dodatky jako výpisy programů,
%%% diagramy apod.). Kaľdá příloha musí být alespoň jednou odkazována z vlastního
%%% textu práce. Přílohy se číslují.
%\chapwithtoc{Attachments}
\appendix
\include{appendix_a}

>>>>

\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\newcommand{\lstfont}{\small\ttfamily}
\lstset{ %
  language=,                % the language of the code
  basicstyle=\lstfont,           % the size of the fonts that are used for the code
  %numbers=left,                   % where to put the line-numbers
  %numberstyle=\tiny\color{gray},  % the style that is used for the line-numbers
  %stepnumber=2,                   % the step between two line-numbers. If it's 1, each line 
                                  % will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},      % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  frame=single,                   % adds a frame around the code
  rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
  tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=t,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
  title=\lstname,                   % show the filename of files included with \lstinputlisting;
                                  % also try caption instead of title
  keywordstyle=\color{blue},          % keyword style
  commentstyle=\color{dkgreen},       % comment style
  stringstyle=\color{mauve},         % string literal style
  escapeinside={\%*}{*)},            % if you want to add a comment within your code
  morekeywords={*,...},              % if you want to add more keywords to the set
}

@@

%%% Přílohy k diplomové práci, existují-li (různé dodatky jako výpisy programů,
%%% diagramy apod.). Kaľdá příloha musí být alespoň jednou odkazována z vlastního
%%% textu práce. Přílohy se číslují.
%\chapwithtoc{Attachments}
\appendix
\include{appendix_a}
\include{appendix_b}

### 2012-03-22 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\begin{lstlisting}[float, caption=Sample query 1., frame=single, label=listing_sample_query_1]
declare namespace local = "http://www.foobar.org";
declare function local:convert($v as xs:decimal?)
  as xs:decimal?
{
  2.20371 * $v (: convert Dfl to Euro :)
};

for $i in /site/open_auctions/open_auction
return local:convert(zero-or-one($i/reserve))
\end{lstlisting}

@@

A syntax tree constructed from sample query in Listing \ref{listing_sample_query_1} is shown in Figure \ref{FIG_syntax_tree_1}.

@@

\subsection{Example}
\begin{lstlisting}[float, caption=Sample query 2., frame=single, label=listing_sample_query_2]
for $p in /site/people/person
let $a :=
  for $t in /site/closed_auctions/closed_auction
  where $t/buyer/@person = $p/@id
  return $t
return <item person="{$p/name/text()}">{count($a)}</item>
\end{lstlisting}

\begin{figure}
\label{FIG_syntax_tree_2}
\caption{Sample syntax tree 2.}
\includegraphics[scale=0.7]{syntax_tree_2.eps}
\end{figure}

Figure \ref{FIG_syntax_tree_2} shows the syntax tree of the query in Listing \ref{listing_sample_query_2}. In this tree, the algorithm founds one occurrence of the join pattern 3. The two for clauses and one where clause which form the occurrence are shown in the red boxes.

>>>>

@@

A syntax tree constructed from sample query in Listing \ref{listing_testing_query_18} is shown in Figure \ref{FIG_syntax_tree_1}.

@@

\subsection{Example}
\begin{figure}
\label{FIG_syntax_tree_2}
\caption{Sample syntax tree 2.}
\includegraphics[scale=0.7]{syntax_tree_2.eps}
\end{figure}

Figure \ref{FIG_syntax_tree_2} shows the syntax tree of the query in Listing \ref{listing_testing_query_8} (subtree of ConstructorNode is omitted because of lack of space). In this tree, the algorithm founds one occurrence of the join pattern 3. The two for clauses and one where clause which form the occurrence are shown in the red boxes.
